\bf Supplementary Results for ``Forecast reconciliation: A geometric view with new insights on bias correction''

### 2020-01-31 Hierarchical-forecast-reconciliation/Supplement/supplement.tex
Supplement George

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx,psfrag,epsf,siunitx, multirow,booktabs}
\usepackage{enumerate}

@@

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering\footnotesize
  \caption{Add caption}
    \begin{tabular}{lrrrrrrrrrrrrr}
    \toprule
    & \multicolumn{6}{c}{Log Transformation}         &       & \multicolumn{6}{c}{Box-Cox Transformation} \\\cmidrule(lr){2-7}\cmidrule(lr){9-14}
    Forecast horizon  & 1     & 2     & 3     & 4     & 5     & 6     &       & 1     & 2     & 3     & 4     & 5     & 6 \\\midrule
          & \multicolumn{13}{c}{RMATE} \\ \cmidrule(lr){2-14}
    Biased Base             & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  &       & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00 \\
    Biased Bottom-up        & 1.76  & 1.69  & 1.73  & 1.72  & 1.64  & 1.60  &       & 1.73  & 1.69  & 1.67  & 1.66  & 1.59  & 1.55 \\
    Biased MinT             & 0.77  & 0.81  & 0.79  & 0.78  & 0.80  & 0.81  &       & 0.77  & 0.78  & 0.77  & 0.75  & 0.79  & 0.80 \\
    Biased OLS              & 0.63  & 0.65  & 0.65  & 0.65  & 0.68  & 0.70  &       & 0.65  & 0.67  & 0.67  & 0.68  & 0.70  & 0.72 \\
    Unbiased Base           & 0.58  & 0.62  & 0.64  & 0.65  & 0.68  & 0.69  &       & 0.73  & 0.75  & 0.76  & 0.77  & 0.78  & 0.79 \\
    Unbiased Bottom-up      & 0.69  & 0.73  & 0.79  & 0.82  & 0.81  & 0.81  &       & 0.84  & 0.86  & 0.88  & 0.90  & 0.88  & 0.87 \\
    Unbiased MinT           & 0.57  & 0.62  & 0.61  & 0.61  & 0.65  & 0.66  &       & 0.70  & 0.71  & 0.71  & 0.70  & 0.74  & 0.75 \\
    Unbiased OLS            & 0.54  & 0.56  & 0.56  & 0.58  & 0.61  & 0.63  &       & 0.67  & 0.69  & 0.69  & 0.70  & 0.71  & 0.72 \\
          & \multicolumn{13}{c}{RMTSE} \\\cmidrule(lr){2-14}
    Biased Base             & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  &       & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00 \\
    Biased Bottom-up        & 1.42  & 1.48  & 1.56  & 1.53  & 1.52  & 1.50  &       & 1.35  & 1.37  & 1.39  & 1.39  & 1.37  & 1.32 \\
    Biased MinT             & 0.97  & 0.98  & 1.02  & 0.98  & 0.98  & 0.98  &       & 0.93  & 0.95  & 0.96  & 0.96  & 0.96  & 0.94 \\
    Biased OLS              & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  &       & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  & 0.97 \\
    Unbiased Base           & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  &       & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  & 0.99 \\
    Unbiased Bottom-up      & 1.18  & 1.21  & 1.27  & 1.24  & 1.23  & 1.20  &       & 1.16  & 1.15  & 1.17  & 1.17  & 1.14  & 1.11 \\
    Unbiased MinT           & 0.93  & 0.94  & 0.97  & 0.94  & 0.94  & 0.93  &       & 0.91  & 0.92  & 0.93  & 0.93  & 0.93  & 0.91 \\
    Unbiased OLS            & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  &       & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  & 0.96 \\\bottomrule
    \end{tabular}
  \label{tab:addlabel}%
\end{table}%
